A demonstration of the \LaTeX\ class file for Wiley NJD Journals\protect\thanks{This is an example for title footnote.}

### 2021-09-07 PrevAdjSurvey.tex

\section{Results}
\subsection{Estimating Prevalence from a Simple Random Sample with an Imperfect Assay}
\subsection{Estimating Prevalence from a Weighted Sample with a Perfect Assay}
\subsection{Estimating Prevalence from a Weighted Sample with an  Imperfect Assay}

>>>>

\section{Results}
\subsection{Estimating Prevalence from a Simple Random Sample with an Imperfect Assay}
\subsection{Estimating Prevalence from a Weighted Sample with a Perfect Assay}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/perfect_coverage_50_0_005_reduced.pdf}
    \caption{Caption}
    \label{fig:perfect_coverage_50_0_005_reduced}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/perfect_coverage_50_0_05_reduced.pdf}
    \caption{Caption}
    \label{fig:perfect_coverage_50_0_05_reduced}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/perfect_coverage_8000_0_005_reduced.pdf}
    \caption{Caption}
    \label{fig:perfect_coverage_8000_0_005_reduced}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/perfect_coverage_8000_0_05_reduced.pdf}
    \caption{Caption}
    \label{fig:perfect_coverage_8000_0_05_reduced.pdf}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/perfect_lower_error_frequency_50_0_005_reduced.pdf}
    \caption{Caption}
    \label{fig:perfect_lower_error_frequency_50_0_005_reduced}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/perfect_lower_error_frequency_50_0_05_reduced.pdf}
    \caption{Caption}
    \label{fig:perfect_lower_error_frequency_50_0_05_reduced}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/perfect_lower_error_frequency_8000_0_005_reduced.pdf}
    \caption{Caption}
    \label{fig:perfect_lower_error_frequency_8000_0_005_reduced}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/perfect_lower_error_frequency_8000_0_05_reduced.pdf}
    \caption{Caption}
    \label{fig:perfect_lower_error_frequency_8000_0_05_reduced.pdf}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/perfect_upper_error_frequency_50_0_005_reduced.pdf}
    \caption{Caption}
    \label{fig:perfect_upper_error_frequency_50_0_005_reduced}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/perfect_upper_error_frequency_50_0_05_reduced.pdf}
    \caption{Caption}
    \label{fig:perfect_upper_error_frequency_50_0_05_reduced}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/perfect_upper_error_frequency_8000_0_005_reduced.pdf}
    \caption{Caption}
    \label{fig:perfect_upper_error_frequency_8000_0_005_reduced}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/perfect_upper_error_frequency_8000_0_05_reduced.pdf}
    \caption{Caption}
    \label{fig:perfect_upper_error_frequency_8000_0_05_reduced.pdf}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/imperfect_coverage_50_0_005_reduced.pdf}
    \caption{Caption}
    \label{fig:imperfect_coverage_50_0_005_reduced}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/imperfect_coverage_50_0_05_reduced.pdf}
    \caption{Caption}
    \label{fig:imperfect_coverage_50_0_05_reduced}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/imperfect_coverage_8000_0_005_reduced.pdf}
    \caption{Caption}
    \label{fig:imperfect_coverage_8000_0_005_reduced}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/imperfect_coverage_8000_0_05_reduced.pdf}
    \caption{Caption}
    \label{fig:imperfect_coverage_8000_0_05_reduced.pdf}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/imperfect_lower_error_frequency_50_0_005_reduced.pdf}
    \caption{Caption}
    \label{fig:imperfect_lower_error_frequency_50_0_005_reduced}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/imperfect_lower_error_frequency_50_0_05_reduced.pdf}
    \caption{Caption}
    \label{fig:imperfect_lower_error_frequency_50_0_05_reduced}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/imperfect_lower_error_frequency_8000_0_005_reduced.pdf}
    \caption{Caption}
    \label{fig:imperfect_lower_error_frequency_8000_0_005_reduced}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/imperfect_lower_error_frequency_8000_0_05_reduced.pdf}
    \caption{Caption}
    \label{fig:imperfect_lower_error_frequency_8000_0_05_reduced.pdf}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/imperfect_upper_error_frequency_50_0_005_reduced.pdf}
    \caption{Caption}
    \label{fig:imperfect_upper_error_frequency_50_0_005_reduced}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/imperfect_upper_error_frequency_50_0_05_reduced.pdf}
    \caption{Caption}
    \label{fig:imperfect_upper_error_frequency_50_0_05_reduced}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/imperfect_upper_error_frequency_8000_0_005_reduced.pdf}
    \caption{Caption}
    \label{fig:imperfect_upper_error_frequency_8000_0_005_reduced}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/imperfect_upper_error_frequency_8000_0_05_reduced.pdf}
    \caption{Caption}
    \label{fig:imperfect_upper_error_frequency_8000_0_05_reduced.pdf}
\end{figure}
